A New Method of Modelling Tuneable Lasers with Functional Composition

### 2019-07-12 Thesis/Previous_Models/Previous.tex
Finished final read through.

\section{Nonlinear Optics}
The standard equation for studying nonlinear optics---which can be derived from the nonlinear wave equation for electric fields\footnote{The derivation is presented in detail in \cite{agrawal2013, ferreira}.}---is
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{t} + i \gamma |A|^2 A - \frac{1}{v_g} \pdiff{A}{t}.
\label{eq:NLoptics}
\end{align}
Here $A = A(z, t) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order---or group delay---dispersion, $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity or Kerr coefficient, and $v_g \in \mathbb{R}^+$ is the group velocity. However, it is customary to transform \eqref{eq:NLoptics} into a comoving reference frame, this is achieved with the substitution
\begin{align}
\label{eq:shift}
T = t - \frac{z}{v_g},
\end{align}
reminiscent of moving to a fixed frame in a free boundary problem \cite{ockendon}. Now, $\pdiff{}{t} \mapsto \pdiff{}{T}$, and $\pdiff{}{z} \mapsto \pdiff{}{z} - \frac{1}{v_g} \pdiff{}{T}$ by chain rule.  Under this transformation, $z$ still defines the distance travelled by the pulse, but, $T$ now designates the time difference from the peak of the pulse for a given $z$. Moreover, $T < 0$ is the leading edge of the pulse, and $T > 0$ is the trailing edge regardless of the actual time elapsed, and because of this, generally $T$ is not very large. Furthermore, the substitution \eqref{eq:shift} cancels the final term of \eqref{eq:NLoptics}, yielding
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A.
\label{eq:smallnlse}
\end{align}
Despite being physically unrelated to quantum mechanics \eqref{eq:smallnlse} is called the \gls{nlse} because of it's functional similarity \cite{agrawal2013, anderson, burgoyne2007, desurvire, ferreira, finot, rothenberg}. \\

@@

In the least complicated case, the modulation and nonlinearity are both omitted giving
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \left( g_0 - \alpha \right) A.
\label{eq:disc1}
\end{align}
This results in a solution in the form of a hyperbolic secant \cite{haus1975, haus1986, haus1992}. On the other hand, including the nonlinearity yields
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \left( g_0 - \alpha \right) A,
\label{eq:disc2}
\end{align}
where a similar solution is found, however, it is instead of the form of a chirped hyperbolic secant \cite{haus1991, usechak}. The nature of the solutions to \eqref{eq:disc1} and \eqref{eq:disc2} is as expected. These equations are slight generalizations of \eqref{eq:smallnlse} which has a soliton solution of a hyperbolic secant \cite{ferreira}. Finally, by including the modulation term, and excluding the nonlinearity we have
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \left( g_0 - \alpha \right) A - \frac{1}{2}M_s T^2.
\end{align}
This can be solved using separation of variables and one finds the solutions are the Gaussian--Hermite polynomials \cite{burgoyne2014, hausbook, haus1975, haus1996, haus2000, kartner, tamura1996, usechak} defined recursively as
\begin{align}
\Her{n}{x} &:= (-1)^n \textrm{e}^{x^2 / 2} \diff[n]{}{x} \textrm{e}^{-x^2},
\label{eq:gaussherm}
\end{align}
However, in practice only the Gaussian is stable---the higher modes quickly decay within the laser \cite{hausbook, haus1975, haus1996, haus2000}. For a more comprehensive history see \cite{haus2000}. \\

@@

Such a method was first proposed in 1955 by Cutler \cite{cutler} while analyzing a microwave regenerative pulse generator. This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, siegman}. Kuizenga and Siegman also had success experimentally validating their model \cite{kuizenga1970b, kuizenga1970}. The effects of the nonlinearity would not be considered until Martinez, Fork, and Gordon \cite{martinez1984, martinez1985} tried modelling passive mode-locking---mode-locking without the use of a modulator. In the absence of a modulator the nonlinearity becomes crucial to shaping the pulse. This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers. In these models the effect of each block is described by a transfer function, for example
\begin{align*}
A_{\text{out}}(T) &= A_{\text{in}}(T) \exp \left( - \frac{\epsilon T^2}{2} \right) \textrm{e}^{i \phi_M - \alpha_M / 2}, \\
\widehat{A_{\text{out}}}(\Omega) &= \widehat{A_{\text{in}}}(\Omega) \exp \left( \frac{i \beta_2 \Omega^2}{2} \right) \textrm{e}^{i \phi_D - \alpha_D / 2}
\end{align*}
for modulation and dispersion, respectively. These transfer functions are then multiplied together to give the overall effect. This is in contrast to the iterative map developed in Sections \ref{sec:comp}--\ref{sec:effects}. \\

>>>>

\section{Nonlinear Optics}
The standard equation for studying nonlinear optics---which can be derived from the nonlinear wave equation for electric fields\footnote{The derivation is presented in detail in \cite{agrawal2013, ferreira}.}---is
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{t} + i \gamma |A|^2 A - \frac{1}{v_g} \pdiff{A}{t}.
\label{eq:NLoptics}
\end{align}
Here $A = A(z, t) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order---or group delay---dispersion, $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity or Kerr coefficient, and $v_g \in \mathbb{R}^+$ is the group velocity. However, it is customary to transform \eqref{eq:NLoptics} into a comoving reference frame, this is achieved with the substitution
\begin{align}
\label{eq:shift}
T = t - \frac{z}{v_g},
\end{align}
reminiscent of moving to a fixed frame in a free boundary problem \cite{ockendon}. Now, $\pdiff{}{t} \mapsto \pdiff{}{T}$, and $\pdiff{}{z} \mapsto \pdiff{}{z} - \frac{1}{v_g} \pdiff{}{T}$ by chain rule.  Under this transformation, $z$ still defines the distance travelled by the pulse, but, $T$ now designates the time difference from the peak of the pulse for a given $z$. Moreover, $T < 0$ is the leading edge of the pulse, and $T > 0$ is the trailing edge regardless of the actual time elapsed, and because of this, generally $T$ is not very large. Furthermore, the substitution \eqref{eq:shift} cancels the final term of \eqref{eq:NLoptics}, yielding
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A.
\label{eq:smallnlse}
\end{align}
Despite being physically unrelated to quantum mechanics \eqref{eq:smallnlse} is called the \gls{nlse} because of its functional similarity \cite{agrawal2013, anderson, burgoyne2007, desurvire, ferreira, finot, rothenberg}. \\

@@

In the least complicated case, the modulation and nonlinearity are both omitted giving
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \left( g_0 - \alpha \right) A.
\label{eq:disc1}
\end{align}
This results in a solution in the form of a hyperbolic secant \cite{haus1975, haus1986, haus1992}. On the other hand, including the nonlinearity yields
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \left( g_0 - \alpha \right) A,
\label{eq:disc2}
\end{align}
where a similar solution is found, however, it is instead of the form of a chirped hyperbolic secant \cite{haus1991, usechak}. The nature of the solutions to \eqref{eq:disc1} and \eqref{eq:disc2} is as expected. These equations are slight generalizations of \eqref{eq:smallnlse} which has a soliton solution of a hyperbolic secant \cite{ferreira}. Finally, by including the modulation term, and excluding the nonlinearity we have
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \left( g_0 - \alpha \right) A - \frac{1}{2}M_s T^2.
\end{align}
This can be solved using separation of variables and one finds the solutions are the Gaussian--Hermite polynomials \cite{burgoyne2014, hausbook, haus1975, haus1996, haus2000, kartner, tamura1996, usechak}, defined recursively as
\begin{align}
\Her{n}{x} &:= (-1)^n \textrm{e}^{x^2 / 2} \diff[n]{}{x} \textrm{e}^{-x^2},
\label{eq:gaussherm}
\end{align}
However, in practice only the Gaussian is stable---the higher modes quickly decay within the laser \cite{hausbook, haus1975, haus1996, haus2000}. For a more comprehensive history see \cite{haus2000}. \\

@@

Such a method was first proposed in 1955 by Cutler \cite{cutler} while analyzing a microwave regenerative pulse generator. This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, siegman}. Kuizenga and Siegman also had success experimentally validating their model \cite{kuizenga1970b, kuizenga1970}. The effects of the nonlinearity would not be considered until Martinez, Fork, and Gordon \cite{martinez1984, martinez1985} tried modelling passive mode-locking---mode-locking without the use of a modulator. In the absence of a modulator the nonlinearity becomes crucial to shaping the pulse. This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers. In these models the effect of each block is described by a transfer function, for example:
\begin{align*}
A_{\text{out}}(T) &= A_{\text{in}}(T) \exp \left( - \frac{\epsilon T^2}{2} \right) \textrm{e}^{i \phi_M - \alpha_M / 2}, \\
\widehat{A_{\text{out}}}(\Omega) &= \widehat{A_{\text{in}}}(\Omega) \exp \left( \frac{i \beta_2 \Omega^2}{2} \right) \textrm{e}^{i \phi_D - \alpha_D / 2},
\end{align*}
for modulation and dispersion, respectively. These transfer functions are then multiplied together to give the overall effect. This is in contrast to the iterative map developed in Sections \ref{sec:comp}--\ref{sec:effects}. \\
